Relative Stable Maps in Genus One via Central Alignments

### 2018-02-02 genus-one-relative-maps.tex
Drew some of the pictures for the Li space example

Consider therefore the following ``object'' of $\VZc{1}{(5)}{\PP^2|\PP^1}{5}$, which \emph{does not} satisfy the novel condition:

>>>>

We proceed by contradiction. Consider a genus one map $C \to \PP^1$ of the following form
\begin{center}
\begin{tikzpicture}
\draw[fill=black] (0,0) node[left]{$E$} -- (4,0);
\draw[fill=black] (0.7,0) circle[radius=2pt] node[below]{$5$};
\draw[fill=black] (2,0) circle[radius=2pt] node[above right]{$2$};
\draw[fill=black] (3,0) circle[radius=2pt] node[above right]{$3$};
\draw (2,1.5) node[right]{$C_1$};
\draw (3,1.5) node[right]{$C_2$};
\draw (2,-1) -- (2,2) node[above]{$2$};
\draw (3,-1) -- (3,2) node[above]{$3$};

\draw[->] (4.5,0) -- (6.5,0);
\draw (5.5,0) node[above]{$f$};
\draw (7,-1) -- (7,2) node[above]{$\PP^1$};
\draw[fill=black] (7,0) circle[radius=2pt] node[right]{$\infty$};
\end{tikzpicture}
\end{center}
and equip the source curve $C$ with a central alignment which identifies the lengths of the components $C_1$ and $C_2$:
\begin{center}
\begin{tikzpicture}
\draw[red,thick,dashed] (0,0) circle[radius=51pt];
\draw[red] (-1.75,0) node[left]{$R_\delta$};
\draw[fill=white] (0,0) circle[radius=4pt];
\draw (0,0.1) node[above]{$E$};
\draw[fill=black] (-1,-1.5) circle[radius=4pt];
\draw (-1.1,-1.5) node[left]{$C_1$};
\draw[fill=black] (-0.1,-0.1) -- (-1,-1.5);
\draw[fill=black] (1,-1.5) circle[radius=4pt];
\draw (1.1,-1.5) node[right]{$C_2$};
\draw[fill=black] (0.1,-0.1) -- (1,-1.5);
\end{tikzpicture}
\end{center}
This defines an ``object'' of $\VZc{1}{(5)}{\PP^1|\infty}{5}$, satisfying all the necessary conditions \emph{except for the novel condition}. We will show that this cannot belong to the image of $\pi_*$.

First we have to identify what the possible lifts of this object to the centrally aligned Li space are.
